Doping-Driven Wettability of Two-Dimensional Materials: a Multiscale Theory

### 2017-08-07 writing/paper-Tian-gr-wetting.tex
Change submission to ACS NANO

% Created 2017-07-24 Mon 23:13
% Intended LaTeX compiler: pdflatex
\documentclass[journal=jacsat,manuscript=article,email=true,hyperref=true,keywords=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{fontspec}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Siyu Li}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Lingling Zhao}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\keywords{two-dimensional materials, doping, wettability, multiscale analysis, MD Simulation, electrical double layer}
\date{}
\title{Doping-Driven Wettability of Two-Dimensional Materials: a Multiscale Theory}
\begin{document}

@@

\newpage{}
\begin{abstract}
  Engineering molecular interactions at two-dimensional (2D) materials
  interfaces enables new technological opportunities in functional
  surfaces and molecular epitaxy.  Understanding the wettability of 2D
  materials represents the crucial first step towards quantifying the
  interplay between the interfacial forces and electric potential of
  2D materials interfaces.  Here we develop the first theoretical
  framework to model the wettability of the doped 2D materials by
  properly bridging the multiscale physical phenomena at the 2D
  interfaces, including: (i) the change of 2D materials surface energy
  (atomistic scale, several \AA), (ii) the molecular reorientation of
  liquid molecules adjacent to the interface (molecular scale,
  \(10^{0}\) \sim \(10^{1}\) nm), and (iii) the electrical double layer
  (EDL) formed in the liquid phase (mesoscopic scale,
  \(10^{0}\) \sim \(10^{4}\) nm).  The latter two effects are found to
  be the major mechanisms responsible for the contact angle change
  upon doping.  When the doping level is electrostatically tuned, we
  demonstrate that 2D materials with high quantum capacitances (e.g.,
  transition metal dichalcogenides, TMDCs) possess a wider range of
  tunability in the interfacial tension.  Furthermore, practical
  considerations such as defects and airborne contamination are also
  quantitatively discussed.  Our analysis implies that the doping
  level can be another variable to modulate the wettability at 2D
  materials interfaces, as well as the molecular packing behavior on a
  2D material-coated surface, essentially facilitating the interfacial
  engineering of 2D materials.
\end{abstract}
% \textbf{Keywords}
% two-dimensional materials, doping, wettability, multiscale analysis, molecular dynamics simulation, electrical double layer
 \maketitle

@@

\section{Introduction}
\label{sec:org5097ce2}

@@

In this report, we propose the first theoretical framework to model
the change of interfacial tension between liquid and a sheet of
monolayer 2D material. Multiscale physical phenomena are considered,
as shown in Figure \ref{fig:scheme-method}. At the atomistic scale
(several \AA{}), we formulate the dependence of surface energy of a 2D
material on the doping density using the quantum capacitance (QC)
calculated by the hybrid density functional theory (DFT) at the level
of Heyd-Scuseria-Ernzerhof functionals (HSE06). Next, the
surface-charge-induced reorientation of liquid molecules adjacent to
the interface is associated with an N-body system, which is resolved
by molecular dynamics (MD) simulations, allowing quantification of the
interfacial tension in the absence of electrolytes in liquid at the
molecular scale (10\(^{\text{0}}\) \textasciitilde{} 10\(^{\text{1}}\) nm). The effect of the electrical
double layer (EDL) induced by the electrostatic interactions between
the 2D material surface charges and the ionic species in liquid, is
then addressed at the continuum level (10\(^{\text{0}}\) \textasciitilde{} 10\(^{\text{4}}\) nm). Practical
considerations, such as the defect density and the surface
contamination are also taken into account to provide a comprehensive
understanding of the phenomena. Finally, we examine and validate our
theory by comparing with the contact angle changes reported in the
electrowetting and the substrate-induced doping experiments.

\section{Results and Discussions}
\label{sec:org177ad24}

\subsection{Surface Energy of Doped 2D Materials}
\label{sec:orge414c66}

@@

\subsection{Reorientation of Liquid Molecules}
\label{sec:org8e3e719}

@@

\subsection{Electrical Double Layer Effect}
\label{sec:org689b84b}

@@

\subsection{Practical Considerations}
\label{sec:orgf8df8eb}

@@

\section{Conclusion}
\label{sec:org950fc3c}

In conclusion, we present a multiscale theoretical framework
concerning the wettability of doped 2D materials, by considering: (i)
the change of 2D materials surface energy, (ii) the molecular
reorientation of liquid molecules adjacent to the interface, and (iii)
the electrical double layer formed in the liquid phase. Taking
graphene as an example, we show that the Coulombic interaction
dominates the change of liquid-2D material interfacial tension, at
both atomistic and continuum length scales.The latter two effects were
found to be the major mechanisms responsible for the water contact angle
change at the 2D material interfaces upon doping.

The doping-induced reorientation of liquid molecules at the
graphene-liquid interface is revealed by MD simulations, which also
allow decoupling of vdW and Coulombic energy contributions to the
interfacial tension in the absence of electrolytes in liquid. It is
found that the interfacial energy change is dominated by the Coulombic
interactions. Our results also reveal an asymmetric change of
graphene-water interfacial energy upon doping, such that slightly
n-doped graphene can reorient interfacial water molecules to minimize
electrostatic attractions, and therefore, slightly increase the
interfacial energy.

On the hand, the EDL effect is calculated by a continuum model. Our
analysis suggests that the reorientation effect is more predominant
than the EDL effect, On the graphene-water interface, we predict that
the combined reorientation and EDL effects can induce a significant
change of the interfacial tension \(\Delta
\gamma_{\mathrm{2D-L}}\), up to -15\textasciitilde{}-20 \(\mathrm{mJ}\cdot
\mathrm{m}^{-2}\), at the doping level of \(\pm 4 \times 10^{13}\ e\cdot
\mathrm{cm}^{-2}\). By adding the fitting parameter concerning the
defect density, our theoretical framework can nicely describe the
experimentally observed doping-induced contact angle change. Finally,
based on the DFT-calculated quantum capacitances (QCs) for a variety
of 2D materials, we predict that the wettability of 2D semiconductors
(e.g., TMDCs) is more tunable under an electric displacement field,
compared with 2D semimetals (e.g. graphene) due to their high quantum
capacitances. Our findings reveal a complete picture for the
modulation of the molecular interactions between liquid and a 2D monolayer upon
doping. The multiscale theoretical
framework proposed here is expected to shed
light on the surface science of 2D materials, 
as well as to provide a quantitative estimation for the wettability
of the doped 2D materials. We hope that the development for the 2D
materials-based functional surfaces in liquid manipulation, energy
harvesting, and molecular epitaxy will be facilitated by the
fundamental principles and theoretical insights presented here.

@@

\newpage{}
\section{Figures}
\label{sec:org801860f}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{../img/dgamma-sigma.pdf}
\caption{\label{fig:dgamma-sigma}
Atomistic scale: \(\Delta \gamma_{\mathrm{2D}}\) as a function of \(\sigma_{\mathrm{2D}}\) for selected 2D materials: graphene, silicene, germanene, phosphorene, MoS\(_{2}\), MoSe\(_{2}\), MoTe\(_{2}\), WS\(_{2}\), WSe\(_{2}\) and WTe\(_{2}\). The 2D semimetals (graphene, silicene and germanene) with low high quantum capcitances show larger decrease of \(\gamma_{\mathrm{2D}}\) upon doping, compared with the 2D semiconductors (TMDCs, phosphorene).}
\end{figure}

>>>>

% Created 2017-08-07 Mon 13:49
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,manuscript=article,email=true,hyperref=true,keywords=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{fontspec}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Siyu Li}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Lingling Zhao}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\keywords{two-dimensional materials, doping, wettability, multiscale analysis, molecular dynamics simulation, electrical double layer}
\date{}
\title{Doping-Driven Wettability of Two-Dimensional Materials: a Multiscale Theory}
\begin{document}

@@

\newpage{}
\begin{abstract}
  Engineering molecular interactions at two-dimensional (2D) materials
  interfaces enables new technological opportunities in functional
  surfaces and molecular epitaxy.  Understanding the wettability of 2D
  materials represents the crucial first step towards quantifying the
  interplay between the interfacial forces and electric potential of
  2D materials interfaces.  Here we develop the first theoretical
  framework to model the wettability of the doped 2D materials by
  properly bridging the multiscale physical phenomena at the 2D
  interfaces, including: (i) the change of 2D materials surface energy
  (atomistic scale, several \AA), (ii) the molecular reorientation of
  liquid molecules adjacent to the interface (molecular scale,
  \(10^{0} \sim 10^{1}\) nm), and (iii) the electrical double layer
  (EDL) formed in the liquid phase (mesoscopic scales,
  \(10^{0} \sim 10^{4}\) nm).  The latter two effects are found to
  be the major mechanisms responsible for the contact angle change
  upon doping.  When the doping level is electrostatically tuned, we
  demonstrate that 2D materials with high quantum capacitances (e.g.,
  transition metal dichalcogenides, TMDCs) possess a wider range of
  tunability in the interfacial tension.  Furthermore, practical
  considerations such as defects and airborne contamination are also
  quantitatively discussed.  Our analysis implies that the doping
  level can be another variable to modulate the wettability at 2D
  materials interfaces, as well as the molecular packing behavior on a
  2D material-coated surface, essentially facilitating the interfacial
  engineering of 2D materials.
\end{abstract}
% \textbf{Keywords}
% two-dimensional materials, doping, wettability, multiscale analysis, molecular dynamics simulation, electrical double layer
 \maketitle

@@

\section{Introduction}
\label{sec:orgd30faa7}

@@

In this report, we propose the first theoretical framework to model
the change of interfacial tension between liquid and a sheet of
monolayer 2D material. Multiscale physical phenomena are considered,
as shown in Figure \ref{fig:scheme-method}. At the atomistic scale
(several \AA{}), we formulate the dependence of surface energy of a 2D
material on the doping density using the quantum capacitance (QC)
calculated by the hybrid density functional theory (DFT) at the level
of Heyd-Scuseria-Ernzerhof functionals (HSE06). Next, the
surface-charge-induced reorientation of liquid molecules adjacent to
the interface is associated with an N-body system, which is resolved
by molecular dynamics (MD) simulations, allowing quantification of the
interfacial tension in the absence of electrolytes in liquid at the
molecular scale (\(10^{0} \sim 10^{1}\) nm). The effect of the electrical
double layer (EDL) induced by the electrostatic interactions between
the 2D material surface charges and the ionic species in liquid, is
then addressed at the continuum level (\(10^{0} \sim 10^{4}\) nm). Practical
considerations, such as the defect density and the surface
contamination are also taken into account to provide a comprehensive
understanding of the phenomena. Finally, we examine and validate our
theory by comparing with the contact angle changes reported in the
electrowetting and the substrate-induced doping experiments.

\section{Results and Discussions}
\label{sec:orgae60da0}

\subsection{Surface Energy of Doped 2D Materials}
\label{sec:org484e298}

@@

\subsection{Reorientation of Liquid Molecules}
\label{sec:org3a835fb}

@@

\subsection{Electrical Double Layer Effect}
\label{sec:org6d3a4a9}

@@

\subsection{Practical Considerations}
\label{sec:orgaf0bbb2}

@@

\section{Conclusion}
\label{sec:org7ecbeb5}

In conclusion, we present a multiscale theoretical framework
concerning the wettability of doped 2D materials, by considering: (i)
the change of 2D materials surface energy, (ii) the molecular
reorientation of liquid molecules adjacent to the interface, and (iii)
the electrical double layer formed in the liquid phase. Taking
graphene as an example, we show that the Coulombic interaction
dominates the change of liquid-2D material interfacial tension, at
both molecular and mesoscopic length scales. The latter two effects were
found to be the major mechanisms responsible for the water contact angle
change at the 2D material interfaces upon doping.

The doping-induced reorientation of liquid molecules at the
graphene-liquid interface is revealed by MD simulations, which also
allow decoupling of vdW and Coulombic energy contributions to the
interfacial tension in the absence of electrolytes in liquid. It is
found that the interfacial energy change is dominated by the Coulombic
interactions. Our results also reveal an asymmetric change of
graphene-water interfacial energy upon doping, such that slightly
n-doped graphene can reorient interfacial water molecules to minimize
electrostatic attractions, and therefore, slightly increase the
interfacial energy. Such asymmetric interfacial energy change arises
from the dipolar nature of water, which implies that the polarities of
liquid and 2D material both determine the symmetry of
doping-driven wettability: the change of interfacial energy upon
doping between nonpolar liquid molecules and homoatomic 2D material is
more symmetric than that between polar liquid and polar 2D
material. We expect that in the latter case, the symmetry of
interfacial energy change would highly depend on the delicate balance
between their degrees of polarization.

On the other hand, the EDL effect is calculated by a continuum model. Our
analysis suggests that the reorientation effect is more predominant
than the EDL effect. On the graphene-water interface, we predict that
the combined reorientation and EDL effects can induce a significant
change of the interfacial tension \(\Delta
\gamma_{\mathrm{2D-L}}\), up to -15 \(\mathrm{mJ}\cdot
\mathrm{m}^{-2}\), at the doping level of \(\pm 4 \times 10^{13}\ e\cdot
\mathrm{cm}^{-2}\). By adding the fitting parameter concerning the
defect density, our theoretical framework can nicely describe the
experimentally observed doping-induced contact angle change. Finally,
based on the DFT-calculated quantum capacitances (QCs) for a variety
of 2D materials, we predict that the wettability of 2D semiconductors
(e.g., TMDCs) is more tunable under an electric displacement field,
compared with 2D semimetals (e.g. graphene) due to their high quantum
capacitances. Our findings reveal a complete picture for the
modulation of the molecular interactions between liquid and a 2D monolayer upon
doping. The multiscale theoretical
framework proposed here is expected to shed
light on the surface science of 2D materials, 
as well as to provide a quantitative estimation for the wettability
of the doped 2D materials. We hope that the development for the 2D
materials-based functional surfaces in liquid manipulation, energy
harvesting, and molecular epitaxy will be facilitated by the
fundamental principles and theoretical insights presented here.

@@

\newpage{}
\section{Figures}
\label{sec:org5261a93}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.75\linewidth]{../img/dgamma-sigma.pdf}
\caption{\label{fig:dgamma-sigma}
Atomistic scale: \(\Delta \gamma_{\mathrm{2D}}\) as a function of \(\sigma_{\mathrm{2D}}\) for selected 2D materials: graphene, silicene, germanene, phosphorene, MoS\(_{2}\), MoSe\(_{2}\), MoTe\(_{2}\), WS\(_{2}\), WSe\(_{2}\) and WTe\(_{2}\). The 2D semimetals (graphene, silicene and germanene) with low high quantum capcitances show larger decrease of \(\gamma_{\mathrm{2D}}\) upon doping, compared with the 2D semiconductors (TMDCs, phosphorene).}
\end{figure}
